### 2016-09-29 rebuttal.tex

\question The word ``software'' in line 91 is ambiguous; ``library'' or ``package'' would make a better choice.
\begin{solution}
We have changed ``software'' to ``library''.
\end{solution}

\question Lines 91--96: ``we discuss/look at/etc'' is the preferred form, instead of ``section discusses/looks at/etc''.
\begin{solution}
We had decided not to use first person.  We prefer to be
consistent here, unless this does violate some journal policy,
which is not the case (see, for example,
\url{https://peerj.com/articles/cs-80/}).
\end{solution}

\question The paragraph in lines 103--105 should be moved to the introduction,
and the footnote from line 104 should be added to that paragraph as a
full-blown sentence, expanded by all the relevant technical information
(Python version, OS, \ldots). Given that the end of life for Python 2 is
2020., a comment on whether all the presented examples work in both Python 2
and 3 should be included as well. Further, emphasise that wildcard imports,
``\texttt{import *}'', should almost never be used in programs (see PEP 8, the
item ``wildcard imports''). The same goes for the \texttt{import} mentioned in lines 484--487.
\begin{solution}
We have moved the footnote inline, and have noted that the examples should
work with Python 2.7, 3.2, 3.3, 3.4, or 3.5, with any operating system that
supports Python.

We have added a footnote discussing the concerns with \texttt{import *} (see
reviewer 2, point~\ref{rev2point1}).
\end{solution}

@@

\question In line 495, the word ``solving'' seems more appropriate than ``solutions''.
\begin{solution}
This was replaced with ``solving ODEs''.
\end{solution}

\question In line 504 ``is'' should be used instead of ``are'' (because ``array'' is singular).
\begin{solution}
This was fixed.
\end{solution}

\question In line 518, ``produces'' should become plural.
\begin{solution}
This was fixed.
\end{solution}

\question The title of section 5, ``Domain specific submodules'', seems inappropriate because the section only covers Physics package (not ``submodules''). It should either be expanded with a short introduction listing other domain specific packages, or it should be renamed to ``Physics package''.
\begin{solution}
\label{rev3point30}
This section was renamed to "Physics submodule".  (See also the
discussion at~\ref{rev3point37} about module vs package).
\end{solution}

@@

\question The word ``symbolics'' in line 528 should be removed (as almost everything in the paper deals with symbolic computation).
\begin{solution}
We have done this.
\end{solution}

\question In line 530, sympy.physics.vector is a module, not a package.
\begin{solution}
The word ``package'' replaced with ``submodule'' (see also point~\ref{rev3point37}).
\end{solution}

### 2016-09-29 rebuttal.tex

\item The SymPy Live section was short and would be mostly duplicated by the
  paragraph that has been added to the introduction in the paper. We have thus
  removed it.
\end{itemize}

We also consider the supplement sections (previously) 2, 3, 4, and
6---``Series'', ``Logic'', ``Diophantine Equations'', and ``Statistics'',
respectively---to be in depth beyond the goals of the main manuscript:

\begin{itemize}
\item The ``Series'' section discusses relatively advanced series expansion methods. We
have added a paragraph detailing basic series expansion to the ``Calculus''
subsection, with a reference to the more detailed section in the supplement.

\item The ``Logic'' section is alluded to in the ``Assumptions'' subsection,
  but is not discussed in depth in the main manuscript. While the logic
  submodule is indeed important for certain parts of SymPy, we do not consider
  it to be of interest to the general reader. Furthermore, on a technical
  note, the assumptions discussed in the manuscript are the so-called ``old
  assumptions'', which do not use the \texttt{sympy.logic} submodule discussed
  in the supplement (they use an implementation of the Rete algorithm, which
  is separate from \texttt{sympy.logic}). The so-called ``new assumptions'',
  mentioned briefly in the ``Conclusion and Future Work'' section, does use
  it, but we have opted to not discuss this module in depth, as it is still in
  development and not fully usable. We have added some text to the assumptions
  section discussing this and referencing the logic subsection of the
  supplement (see footnote~\ref{P-note:assumptions}).

@@

We have added a footnote discussing the concerns with \texttt{import *} (see
reviewer 2, point~\ref{rev2point1}).
\end{solution}

\question Line 119 should be removed, as it is basically a copy of the previous line.
\begin{solution}
Line 119 is the output of line 118, so not showing it would
be incorrect.

The aim here was simply to show that the input expression remains unevaluated.
We have added a sentence before the example to note this.
This particular example was chosen because it shows the basic syntax for
addition, subtraction, multiplication, division, and exponentiation.
\end{solution}

\question In line 121 the word ``stored'' should be replaced by ``used as keys''.
\begin{solution}
See the next answer.
\end{solution}

\question What do the authors mean by ``thereby permitting features such as caching'' in line 122? Caching can be done for mutable types as well, just not through hashing.
\begin{solution}
This paragraph was replaced by:
\begin{quote}
Importantly, SymPy expressions are immutable. This simplifies the design of
SymPy by allowing expression interning. It also enables expressions to be
hashed, which is used to implement caching in SymPy.
\end{quote}
\end{solution}

### 2016-09-29 assumptions.tex
Better wording
XRef the assumptions footnote to the rebuttal

Basic implications between the facts are used to deduce assumptions.
Deductions are made using the Rete
algorithm~\cite{doorenbos1995production}.\footnote{For historical reasons,
  this algorithm is distinct from the \texttt{sympy.logic} submodule, which is
  discussed in the supplementary material. SymPy has an experimental
  assumptions system which stores facts separate from objects, and uses
  \texttt{sympy.logic} and a SAT solver for deduction. We will not discuss
  this system here.} For instance, the assumptions system knows that being an
integer implies being rational.
\begin{verbatim}
>>> i = Symbol('i', integer=True)
>>> i.is_rational
True
\end{verbatim}
Furthermore, expressions compute the assumptions on themselves
based on the assumptions of their arguments. For instance, if \texttt{x} and
\texttt{y} are both created with \texttt{positive=True}, then
\texttt{(x + y).is\_positive} will be \texttt{True} whereas
\texttt{(x - y).is\_positive} will be \texttt{None}.

>>>>

Basic implications between the facts are used to deduce assumptions.
Deductions are made using the Rete
algorithm~\cite{doorenbos1995production}.\footnote{\label{note:assumptions}For historical reasons,
  this algorithm is distinct from the \texttt{sympy.logic} submodule, which is
  discussed in the supplementary material. SymPy also has an experimental
  assumptions system which stores facts separate from objects, and uses
  \texttt{sympy.logic} and a SAT solver for deduction. We will not discuss
  this system here.} For instance, the assumptions system knows that being an
integer implies being rational.
\begin{verbatim}
>>> i = Symbol('i', integer=True)
>>> i.is_rational
True
\end{verbatim}
Furthermore, expressions compute the assumptions on themselves
based on the assumptions of their arguments. For instance, if \texttt{x} and
\texttt{y} are both created with \texttt{positive=True}, then
\texttt{(x + y).is\_positive} will be \texttt{True} whereas
\texttt{(x - y).is\_positive} will be \texttt{None}.
